Summary Tables

### 2022-10-12 summary_tables.Rmd
adding mock scenarios for africa and india; updating input parameters fro Africa

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
NSCEN <- 4
#cities <- c('accra','sao_paulo','buenos_aires')

>>>>

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- F
AFRICA_INDIA = T
NSCEN <- 4
#cities <- c('accra','sao_paulo','buenos_aires')
